Tree establishment in models of forest dynamics: a key priority for further research

### 2023-03-12 manuscript/manuscriptRW.Rmd
redefine thresholds in the observed data

The starting point for the models establishment differs as well, ranging
from seedbank, seed or seedling to sapling (i.e., trees much larger than
10 cm height, often at least 2-3 m tall). Models that start from seed
need to include a larger number of ecological processes such as
germination and survival of young seedlings, whereas models that started
from saplings have to aggregate via parameterizations several ecological
processes because they are not treated explicitly. This reduces model
complexity but comes at the cost of blurring process representation. In
the models used in this study the overall complexity in the
establishment modules varies considerably. Following @bugmann2022, we
can classify seven models (iLand, PICUS, LandClim, ForCEEPS, LPJ-GUESS,
ForClim and TreeMig) as having rather high complexity in their
establishment modules (mean establishment formulation complexity
complexity across all processes \>0, Table
\@ref(tab:)\@ref(tab:tableModels)).

@@

We selected 200 sites from this network as the benchmarking dataset for
the simulation. The selection of sites is representative for the
environmental variation of the data. This was achieved by applying
k-means clustering to define 200 clusters of plots from the original set
of 869 plots along the environmental dimensions of temperature, water
balance, soil quality and exposition (i.e., slope and aspect). Each of
these sites featured at least two consecutive measurements. Ingrowth was
measured at threshold of 7 and 10 cm of stem diameter at breast height
in all sites except for 35 sites where only ingrowth at the 10 cm
diameter threshold was available. Plot size ranged from 0.02 ha to 5.52
ha, and the data were further processed and aggregated following
@käber2022 to provide ingrowth rates per ha and per decade. The
observations used in this study featured 30,900 established trees, and
ingrowth rates per site, sample and decade ranged from zero to 1246
trees per ha, with a mean of 56 trees per ha. For more details on this
unique dataset and the detailed establishment information, cf.
@käber2022.

>>>>

The starting point for the models establishment differs as well, ranging
from seedbank, seed or seedling to sapling (i.e., trees much larger than
10 cm height, often at least 2-3 m tall). Models that start from seed
need to include a larger number of ecological processes such as
germination and survival of young seedlings, whereas models that started
from saplings have to aggregate via parameterizations several ecological
processes because they are not treated explicitly. This reduces model
complexity but comes at the cost of blurring process representation. In
the models used in this study the overall complexity in the
establishment modules varies considerably. Following @bugmann2022, we
can classify seven models (iLand, PICUS, LandClim, ForCEEPS, LPJ-GUESS,
ForClim and TreeMig) as having rather high complexity in their
establishment modules (mean establishment formulation complexity
complexity across all processes \>0, Table \@ref(tab:tableModels)).

@@

We selected 200 sites from this network as the benchmarking dataset for
the simulation. The selection of sites is representative for the
environmental variation of the data. This was achieved by applying
k-means clustering to define 200 clusters of plots from the original set
of 869 plots along the environmental dimensions of temperature, water
balance, soil quality and exposition (i.e., slope and aspect). Each of
these sites featured at least two consecutive measurements. Ingrowth
thresholds for the sites differed between 0 and 10 cm, we defined two
data sets where one included all sites with a dbh threshold of 7cm or
lower and the other included another 35 sites with dbh thresholds
between 7 and 10 cm. Thus we focused on two data sets with the
harmonized dbh thresholds of 7 cm and 10 cm.

Plot size ranged from 0.02 ha to 5.52 ha, and the data were further
processed and aggregated following @käber2022 to provide ingrowth rates
per ha and per decade. The observations used in this study featured
30,900 established trees, and ingrowth rates per site, sample and
decade ranged from zero to 1246 trees per ha, with a mean of 56 trees
per ha. Adult species composition was also available for the simulated
species. For more details on this unique dataset and the detailed
establishment information, cf. @käber2022.
